\documentclass[letterpaper,10pt]{article}

\usepackage{geometry}
\usepackage{hyperref}
\usepackage{glossaries}
\usepackage[pdftex]{graphicx}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{color}
\geometry{textheight=8.5in, textwidth=6in}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=bash,
    aboveskip=3mm,
      belowskip=3mm,
	showstringspaces=false,
	  columns=flexible,
	    basicstyle={\small\ttfamily},
	      numbers=none,
	        numberstyle=\tiny\color{gray},
		  keywordstyle=\color{blue},
		    commentstyle=\color{dkgreen},
		      stringstyle=\color{mauve},
		        breaklines=true,
			  breakatwhitespace=true,
			    tabsize=3
			    }

\title{Final Project: Bug Report - Hendriri Dominion Implementation}
\author{Helena~Bales\\ \\ CS362-001 \\ Winter 2017}

\parindent = 0.0 in
\parskip = 0.1 in

\begin{document}
\maketitle

\clearpage
\tableofcontents
\clearpage

\section{Introduction}
This document is a Bug Report as part of the CS362 Final Project on Mutation Testing. This document 
reports the presence of two bugs in a classmate's, hendriri's, implementation of Dominion. The 
Dominion implementation was pulled from the class Github repository on March 19th, 2017.

\section{Bugs}
\subsection{Bug 1 - Card - Smithy}
\subsubsection{Error Message}
This is the error message that was returned when running the tests through Maven.

\begin{lstlisting}
Smithy(org.cs362.dominion.CardTest): expected:<7> but was:<8>
\end{lstlisting}

\subsubsection{Bug Location}
The test that did not pass was the Test called Smithy() in CardTest. I found that the following line 
in CardTest is the assertion that did not pass. It is checking the hand size for player 1 after 
playing a Kingdom card.

\begin{lstlisting}
assertEquals(player1.hand.size(), 8);
\end{lstlisting}

In order to find the bug, I looked at the Smithy() function in Card.java. In this function, I found 
the bug that hendriri had introduced. The Smithy() function only drew two new cards when it was 
supposed to draw 3. 

\subsubsection{Solution}
This bug is very easy to fix as all it requires is to draw one more card in the 
Smithy function in Card.

\subsection{Bug 2 - Card - Baron}
\subsubsection{Error Message}
This is the error message that was returned when running the tests through Maven.

\begin{lstlisting}
BaronTEST1(org.cs362.dominion.CardTest): expected:<3> but was:<4>
\end{lstlisting}

\subsubsection{Bug Location}
The test that did not pass was the test called BaronTEST1() in CardTest. I found that the following line in CardTest is the assertion that did not pass. It is checking for the number of coins after 
playing a kingdom card.

\begin{lstlisting}
assertEquals(player1.coins, 4);
\end{lstlisting}

In order to find the bug, I looked at the Baron() function in Card.java. In this function, I found the
 bug that henriri had introduced. The Baron() function adds one too few coins, resulting in the player
 having three and needing four.

\subsubsection{Solution}
This is a very easy bug to fix. On line 253 of Card.java, the 3 should be changed to a 4.

\section{Conclusion}
The bugs reported in this document are both off-by-one errors that were found through Unit Testing of 
hendriri's Domnion Implementation. They are both located in the Card.java file. They can easily both 
be fixed by changing the two functions Baron() and Smithy().
\end{document}
